Syntax-Based Concept Alignment for Domain-Specific Machine Translation

### 2021-05-09 paper/paper.tex
tentative abstract

\begin{document}
\maketitle
\begin{abstract}
% TODO: abstract
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
In grammar-based domain-specific machine translation, constructing high-quality translation lexica is a crucial but time consuming task requiring significant linguistic knowledge. 
In presence of a corpus of parallel example sentences, statistical word and phrase alignment tools allow to automate part of this process, but are not suitable for small datasets and often fail to identify discontinuous multiword correspondences. 
Addressing both problems, we propose a data-driven, syntax-based approach to the automation of this task and put it to the test in a simple grammar-based translation pipeline.
\end{abstract}
